Name matching through deep learning

### 2018-12-10 old/paper2018/introduction2.tex
more edits

We compared also compared multiple proposed local loss functions: triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} along with an adaptation of the triplet loss function for both sorts of datasets.  The main finding here was that the effectiveness of the loss function varied by dataset.  For the harder problem of learning people's names, an adaptation of triplet loss worked best, whereas for easier problem of company names learning, Schroff produced the best learning.

>>>>

We compared also compared multiple proposed local loss functions: triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} along with an adaptation of the triplet loss function for both sorts of datasets.  The main finding here was that the effectiveness of the loss function varied by dataset.  For the harder problem of learning people's names, an adaptation of triplet loss worked best, whereas for easier problem of company names learning, triplet loss produced the best learning.  We provide the models, code, and datasets\footnote{\url{https://github.com/yehudagale/fuzzyjoiner}} for re-use.

### 2018-12-10 old/paper2018/siamese_networks.tex
llncs stuff for eswc
figure hacking
more edits

\section{Network Architecture}
\label{architecture}
\begin{figure}
\includegraphics[width=1.0\linewidth]{triplet_siamese_network}
\caption{Architecture of the siamese network}
\label{siamese_nets}
\end{figure}

Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we implemented to build the models using Keras and Tensorflow.  As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.  During the tokenization process, we kept punctuation such as `-', `,', and `.' in the name because they are important signals in processing a name.  For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity.  A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  We used character rather than word embeddings primarily because many names were missing from word based vector embeddings.

These three input character embedding vectors were fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.  GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.  For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.

@@

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.31\linewidth}
        \centering
        \includegraphics[width=\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.31\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.31\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure}

>>>>

\section{Network Architecture}
\label{architecture}
\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{triplet_siamese_network}
\end{center}
\caption{Architecture of the siamese network}
\label{siamese_nets}
\end{figure}

Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we implemented to build the models using Keras and Tensorflow.  As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.  Our first step was to convert these into input vectors, one for each name part.  We tokenized the name, keeping punctuation such as `-', `,', and `.' because they are important signals in processing a name.  For the network, input vectors are computed for each entity assuming a maximum name length of 10 name parts for each entity.  A 100 dimensional character embedding was computed for each name part in the entity name using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  We used character rather than word embeddings primarily because many names were missing from word based vector embeddings.

These three input character embedding vectors were fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.  GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.  For name and textual data, positional information of name parts is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.

@@

\begin{figure}[htb]
    \subfloat[Triplet loss\label{schroff_loss}]{%
        \includegraphics[width=.3\linewidth]{schroff_triplet}
     }
    ~ 
    \subfloat[Triplet loss\label{modified_loss}]{%
        \includegraphics[width=.3\linewidth]{modified_loss}
     }
    ~ 
    \subfloat[Triplet loss\label{angular_loss}]{%
        \includegraphics[width=.3\linewidth]{angular_loss}
     }
\end{figure}
